Molecular Analysis

### 2023-10-17 analysis/aud_analysis.Rmd
add posterior probabilities to plots

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "b", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "d", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

### 2023-10-17 analysis/mol_analysis.Rmd
add posterior probabilities to plots

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = 1, xend = 1, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 65%", y_position = 28, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

>>>>

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")
